Equalizer Programming Guide

### 2007-11-16 Developer/ProgrammingGuide/paper.tex
Update Programming Guide
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\title{Equalizer Programming Guide\\
  {\vspace{-1ex}\footnotesize\sffamily\mdseries
    \htmladdnormallink{http://www.equalizergraphics.com/documents/Developer/ProgrammingGuide.pdf}
    {http://www.equalizergraphics.com/documents/ProgrammingGuide.pdf}}
}
\author{Eyescale Software GmbH}

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.1.0 for Equalizer 0.4+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.0.1   & Nov 06, 2007 & Fixed Typo\\
    1.1     & Nov 12, 2007 & Adapted distributed objects\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

>>>>

\title{Equalizer Programming Guide}
\author{Eyescale Software GmbH}

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.1.1 for Equalizer 0.4+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.0.1   & Nov 06, 2007 & Fixed Typo\\
    1.1     & Nov 12, 2007 & Adapted distributed objects\\
    1.1.1   & Nov 16, 2007 & Minor improvements based on lulu.com print\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage
